Further Explorations of \suldiox~Aqueous Adsorption:

### 2011-08-31 Introduction.tex
old?

As a model gas, \suldiox~has been used extensively in research because of its importance in commercial and environmental systems. The molecular structure, high solubility in water, and its abundance make it a pivotal compound in numerous aqueous atmospheric reactions. A complete picture of the \suldiox~adsorption process will aide in understanding gaseous adsorption on the many aqueous surfaces in the environment, as well as in understanding the fundamental nature of gases in water interfacial regions.

>>>>

As a model gas, \suldiox~has been used extensively in research because of its importance in commercial and environmental systems.\cite{Boniface2000,Jayne1990,Johns2011,Heber1997,Faloona2009,Clegg2001} The molecular structure, high solubility in water, and its abundance make it a pivotal compound in numerous aqueous atmospheric reactions. A complete picture of the \suldiox~adsorption process will aide in understanding gaseous adsorption on the many aqueous surfaces in the environment, as well as in understanding the fundamental nature of gases in water interfacial regions.
